Collaborative Visual Analysis on the Web with RCloud

### 2015-03-31 casestudies.tex
work on conclusions

In this section, we present a simple, but real-world example
application currently deployed using RCloud.

This example application is an implementation of LDAVis, a
recently-published method for visualizing large collections of
text. It was specifically designed to enable non-expert users to
explore collections of short text documents using topic modeling and
visualization. Topic modeling~\cite{Blei:2003:LDA} is a standard
technique for text summarization which, although powerful, requires a
certain amount of manual intervention and
interpretation~\cite{Sievert:2014:LAM}.

@@

LDAVis itself was developed by two members of the technical staff at
AT\&T Labs, and originally targeted RStudio's
Shiny~\cite{RStudio:2013:SWA}, a framework for developing R
applications for the web.  While Shiny provides unparalleled ease of
development, discoverability and deployment turn out to be equally
important aspects in the lifecycle of an internal application (see
Section~\ref{sec:interviews}).  On these aspects, RCloud provides a
very simple model: \emph{all developed notebooks are automatically
  deployed}.

LDAVis combines textual analysis, dimensionality reduction, and
interactive visualization. The text analysis is performed via a
combination of an existing R library that fits an LDA model using
Gibbs sampling~\cite{} and some R code written specifically by the
developers. The analysis module is, ultimately, a single R function
that is exposed to the web application via the Javascript-R RPC
mechanism described in Section~\ref{sec:system}; this way, the
analysis is executed remotely on the RCloud servers.

>>>>

In this section, as an example we present a simple real-world
application that was deployed under RCloud.

The application is an implementation of LDAVis, a
recently-published method for visualizing large text corpora.
It was specifically designed to assist non-experts to explore
collections of short text documents using topic modeling and
visualization. Topic modeling~\cite{Blei:2003:LDA} is a standard
technique for text summarization which, although powerful, requires a
certain amount of manual intervention and
interpretation~\cite{Sievert:2014:LAM}.

@@

LDAVis was developed by two technical staff members at
AT\&T Labs, and originally targeted RStudio's
Shiny~\cite{RStudio:2013:SWA}, a framework for developing R
applications for the web.  While Shiny provides outstanding ease of
development, discoverability and deployment turn out to be equally
important aspects in the lifecycle of an internal application (see
Section~\ref{sec:interviews}). On these aspects, RCloud provides a
very simple model: \emph{all developed notebooks are automatically
  deployed}.

LDAVis combines text analysis, dimensionality reduction and
interactive visualization. Text analysis is performed via a
combination of an existing R library that fits an LDA model using
Gibbs sampling~\cite{} and some R code written specifically by the
developers. The analysis module is, ultimately, a single R function
that is exposed to the web application via the Javascript-R RPC
mechanism described in Section~\ref{sec:system}; this way, the
analysis is executed remotely on the RCloud servers.

### 2015-03-31 conclusion.tex
work on conclusions

\stephen{Is this the kind of bad conclusion that contains
a lot of material that should have been explained at the
beginning of the paper to move it along faster and tell
people why they should be interested in the work? What
would be our conclusion?  These capabilties are important,
but they are really hard to program, and adoption is slow
because you're meddling with people's work process and
toolset, which is the heart of their environment and
not some little toy you provide out on the fringes.
Infrastructure is hard.}

@@

Building on previous work to define requirements for
visual analytics, we designed a prototype environment, RCloud.
RCloud supports collaboration and communication
through shared experimental workbooks with version
control, searching, recommending, annotating, and publishing
experiments as web sites and as reusable services.

We also deployed RCloud in a community of working data scientists.
Experience with the RCloud prototype provides evidence that data
science teams and the organizations in which they work benefit from
having capabilities that support collaboration and integrate
the entire visual analytics process.

RCloud is a step toward practical ``DevOps for data science'' and
reproducible, publishable experiments.

Possible next steps are
to incorporate richer recommendation techniques, to provide fine-grained
information security, and to improve the usability of the human interface.

>>>>

@@

Building on previous work to define requirements for
visual analytics, we designed an environment
for exploration, sharing, presentation and publishing.
We implemented it in the RCloud prototype.

We deployed RCloud in a community of working data scientists.
Experience with the RCloud prototype provides evidence that data
science teams and the organizations in which they work benefit from
having capabilities that support collaboration and integrate
the entire visual analytics process. Specifically, features for
sharing and publishing were eagerly adopted. Features for data
single-user data exploration, that compete with existing mature
tools, were not accepted as readily. Some experienced users
fashioned their own workflow so they could keep using familiar EDA tools.

The study has provided a step toward practical ``DevOps for data science''
and reproducible, publishable experiments.  Possible next steps are
to incorporate richer recommendation techniques, to provide fine-grained
information security, and to improve the usability of the human interface.
